Power simulation section

### 2023-08-08 docs/manuscript.Rmd
work on lme4 section

<!-- describe the lme4 package and how it works-->
The lme4 R package is a state-of-the-art tool for fitting frequentist Generalized Linear Mixed Models (GLMMs). It provides extensive capabilities for modeling complex data structures, including models with normally distributed random intercepts and random slopes. The package includes a useful function called "simulate" that allows researchers to simulate the dependent variable based on the same model formula used for model fitting, enabling power simulations and other related analyses.

In lme4, the parameterization used involves the concept of both the beta vector and the theta vector. When considering only random intercepts, the theta parameter represents the standard deviation of the random intercepts, providing information about the variability across the different levels of the random effect. This allows for a deeper understanding of the random intercepts' influence on the outcome variable.

Regarding random slopes, the interpretation of theta becomes more complex. It encompasses the covariance structure between the random slopes and the random intercepts. The theta vector accounts for the variability and correlation between these different random effects, offering insights into the multilevel nature of the data. However, it is important to note that the tutorial discussed in this paper focuses solely on the simpler case of random intercepts, while acknowledging the more intricate implications of theta in models involving random slopes.

>>>>

<!-- describe the lme4 package and how it works-->
The lme4 R package is a state-of-the-art tool for fitting frequentist GLMMs (for Bayesian GLMMs, the brms R package is currently the most prominent option).
The lme4 package includes a useful function called "simulate" that allows researchers to simulate the dependent variable based on the same model formula used for model fitting, enabling power simulations and other related analyses.
However, the model parameterization used by the lme4 package is quite technical, making it more difficult for applied researchers to determine whether their specified population model implies plausible associations in their simulated data.
Therefore in this tutorial, we simulate data for GLMMs from first principles to assist applied researchers in better understanding all model assumptions, and then use lme4 to analyze the simulated datasets.
